Deep Probabilistic Models for Camera Geo-Calibration

### 2018-10-01 chapters/introduction/introduction.tex
add one more citation to deternimistic system
fix a duplicate reference img2gps

Most recent geo-calibration algorithms are deterministic
systems~\cite{baatz2012large,doersch2012what,li2012worldwide}.
Deterministic systems have some obvious drawbacks: 1) they cannot
model the inherent uncertainties from images of ambiguous scenes, and
2) without a proper modeling of the uncertainty, the subsequent
process can yield overly confident predictions. To address these
problems, we propose to build probabilistic systems for camera
geo-calibration.

@@

\item \textbf{Geo-Localization:}
The task of geo-localization estimates the geographic location, $(lat,
lon)$, of the camera given image/video inputs.
%
As an important step of geo-localization, extracting
location-dependent features from image data has drawn a great detail
of attention from the vision community~\cite{jacobs07geolocate,
jacobs11geolocate, jacobs08geoorient}. The common trend amongst these
methods is that they take advantage of a large dataset of
geo-referenced images. Hays and Efros~\cite{hays2008im2gps} use a
data-driven scene matching approach to localize a query image using a
large dataset of geo-tagged images.  Doersch
\etal~\cite{doersch2012what} extract location-dependent features that
capture the relative appearance differences of large cities.  Lin et
al.~\cite{lin2013cross} localize a ground-level image by learning the
relationship between pairs of ground and aerial images \footnote{In
the context of our thesis, we do not distinguish between satellite
imagery and aerial imagery} of the same location. Other techniques
focus on urban environments and infer location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}.  Many
other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
\newline

>>>>

Most recent geo-calibration algorithms are deterministic
systems~\cite{baatz2012large,doersch2012what,li2012worldwide,kendall2015convolutional}.
Deterministic systems have some obvious drawbacks: 1) they cannot
model the inherent uncertainties from images of ambiguous scenes, and
2) without a proper modeling of the uncertainty, the subsequent
process can yield overly confident predictions. To address these
problems, we propose to build probabilistic systems for camera
geo-calibration.

@@

\item \textbf{Geo-Localization:}
The task of geo-localization estimates the geographic location, $(lat,
lon)$, of the camera given image/video inputs.
%
As an important step of geo-localization, extracting
location-dependent features from image data has drawn a great detail
of attention from the vision community~\cite{jacobs07geolocate,
jacobs11geolocate, jacobs08geoorient}. The common trend amongst these
methods is that they take advantage of a large dataset of
geo-referenced images. Hays and Efros~\cite{im2gps} use a
data-driven scene matching approach to localize a query image using a
large dataset of geo-tagged images.  Doersch
\etal~\cite{doersch2012what} extract location-dependent features that
capture the relative appearance differences of large cities.  Lin et
al.~\cite{lin2013cross} localize a ground-level image by learning the
relationship between pairs of ground and aerial images \footnote{In
the context of our thesis, we do not distinguish between satellite
imagery and aerial imagery} of the same location. Other techniques
focus on urban environments and infer location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}.  Many
other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
\newline

### 2018-10-01 chapters/mcmc/paper.tex
fix a duplicate reference img2gps

However, recognizing the geo-location and geo-orientation of an
arbitrary outdoor image is an extremely challenging task.  Many
methods have been proposed; the most common approach is to build a
large database of images with known location and localize a query
image using either local~\cite{li2010location,schindler2008detecting}
or global~\cite{hays2008im2gps,doersch2012what} image features.  This
approach is not applicable when no nearby ground-level imagery exists
in the reference database, such as when the image was not captured
near a popular tourist destination.  Even
when reference imagery is available, the appearance of the objects may
not be visually distinctive, for example a train track or a body of
water.

@@

Extracting location-dependent features from image data has drawn a
great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch et al. extract location-dependent features that
capture the relative appearance differences of large cities.  Lin et
al.~\cite{lin2013cross} localize a ground-level image by learning the
relationship between pairs of ground and aerial images of the same
location. Other techniques focus on urban environments and infer
location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.

>>>>

However, recognizing the geo-location and geo-orientation of an
arbitrary outdoor image is an extremely challenging task.  Many
methods have been proposed; the most common approach is to build a
large database of images with known location and localize a query
image using either local~\cite{li2010location,schindler2008detecting}
or global~\cite{im2gps,doersch2012what} image features.  This
approach is not applicable when no nearby ground-level imagery exists
in the reference database, such as when the image was not captured
near a popular tourist destination.  Even
when reference imagery is available, the appearance of the objects may
not be visually distinctive, for example a train track or a body of
water.

@@

Extracting location-dependent features from image data has drawn a
great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch et al. extract location-dependent features that
capture the relative appearance differences of large cities.  Lin et
al.~\cite{lin2013cross} localize a ground-level image by learning the
relationship between pairs of ground and aerial images of the same
location. Other techniques focus on urban environments and infer
location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
